Gaia identifies VFTS682 as the most massive runaway star known to date

### 2018-05-12 VFTS682.tex
minor

Recently, \citet{platais:18} used multi-epoch Hubble Space
Telescope imaging to identify and shed new light on runaway stars from
the 30 Doradus region based on proper motion measurements. In this study we report on our analysis of the data from the second Gaia data release (DR2) \cite[][]{gaia:16,brown:18}.  We combine the radial velocity measurements from the VFTS survey \citep[][]{evans:11} with the proper motion from Gaia DR2 to reconstruct the three-dimensional velocity of VFTS682, and test the hypothesis that this star was ejected from R136.

Our results indicate that VFTS 682 is a bona fide runaway star. The direction and magnitude of the velocity vector are fully consistent with dynamical ejection from R136.  Its inferred age is consistent with the inferred travel time. This means that the hypothesis that VFTS 682 is formed in relative isolation is rejected.  This makes VFTS 682, with an inferred present day mass well above a hundred solar masses, the most massive runaway star known to date.

>>>>

Recently, \citet{platais:15,platais:18} used multi-epoch Hubble Space
Telescope imaging to identify and shed new light on runaway stars from
the 30 Doradus region based on proper motion measurements. In this study we report on our analysis of the data from the second Gaia data release \cite[DR2,][]{gaia:16,brown:18}.  We combine the radial velocity measurements from the VFTS survey \citep[][]{evans:11} with the proper motion from Gaia DR2 to reconstruct the three-dimensional velocity of VFTS682, and test the hypothesis that this star was ejected from R136.

Our results indicate that VFTS 682 is a bona fide runaway star. The
direction and magnitude of the velocity vector are consistent with
dynamical ejection from R136. The age inferred from the spectral
analysis \citep[from][]{schneider:18} is consistent with the travel
time we calculate for this star. Therefore, the hypothesis that VFTS
682 is formed in relative isolation is rejected.  This makes VFTS 682, with an inferred present day mass well above a hundred solar masses, the most massive runaway star known to date.
